Urban Connectivity Dynamics: Analyzing Free Public WiFi Distribution in Toronto

### 2024-04-17 outputs/paper/paper.qmd
create new date frame for final usage

In this section, I will explore the diverse modes of `R`-based data collection and generation within the `RStudio` environment [@citeR; @citeRStudio]. The data under scrutiny in this paper originates from the `opendatatoronto` R package [@citeODT], specifically drawing from the Toronto fire incidents dataset. The analysis benefits from additional functionalities harnessed from various R packages such as `tidyverse` [@citeTidyverse], `here` [@citeHere], `readr` [@citeReadr], `ggplot2` [@citeGgplot2], `knitr` [@citeKnitr], and `dplyr` [@citeDplyr]. Further insights into the deployment of these packages will be expounded upon in the ensuing subsections.

## Location and description data of Toronto free public WiFi

@@

## 2021 Ward Profiles based on the 25-Ward model

@@

>>>>

In this section, I will explore the diverse modes of `R`-based data collection and generation within the `RStudio` environment [@citeR; @citeRStudio]. The data under scrutiny in this paper originates from the `opendatatoronto` R package [@citeODT], specifically drawing from theLocation and description data of Toronto free public WiFi dataset, as well as the 2021 Ward Profiles based on the 25-Ward model dataset. The analysis benefits from additional functionalities harnessed from various R packages such as `tidyverse` [@citeTidyverse] installed to gain access to other important R packages, `here` [@citeHere] created a path to specific saved files, `readr` [@citeReadr] read and imported data, `ggplot2` [@citeGgplot2] made the data visualizations, `knitr` [@citeKnitr] and `dplyr` [@citeDplyr] manipulated and cleaned data, and `modelsummary` [@citemodelSummary] to create summary tables. Further insights into the deployment of these packages will be expounded upon in the ensuing subsections.

## First Dataset: Location and description data of Toronto free public WiFi

@@

## Second Dataset: 2021 Ward Profiles based on the 25-Ward model

@@

## Variables of Interest
